Working memory performance in adverse environments: Enhanced, impaired, or intact?

### 2023-10-26 README.qmd
final version of readme

---
title: "Working memory performance in adverse environments: Enhanced, impaired, or intact?"
output: 
  github_document:
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=F, echo=F}
library(tidyverse)
devtools::load_all("D:/repositories/projectlog")
#source('scripts/dependencies.R')
knitr::opts_chunk$set(echo = F, message = F, warning = F)

```
<br>
This repository contains data, code, and output for a project entitled "Working memory performance in adverse environments: Enhanced, impaired, or intact?". A Stage 1 snapshot of the project has been submitted to [Peer Community in Registered Reports (PCI-RR)](https://rr.peercommunityin.org/)

@@

flextable::flextable(proj_history) |> 
  flextable::autofit() |> 
  flextable::compose(
    j = "milestone",
    value = flextable::as_paragraph(
      flextable::hyperlink_text(x = milestone, url = milestone_link)
    )
  ) |> 
  flextable::compose(
    j = "link",
    value = flextable::as_paragraph(
      flextable::hyperlink_text(x = "Click here", url = commit_link)
    )
  ) |> 
  flextable::delete_columns(c("ref", "milestone_hash", "commit_hash", "files", "merge", "milestone_link", "commit_link"))
```

>>>>

---
title: "Working memory performance in adverse environments: Enhanced, impaired, or intact?"
output: github_document
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=F, echo=F}
library(tidyverse)
devtools::load_all("D:/repositories/projectlog")
#source('scripts/dependencies.R')

knitr::opts_chunk$set("ft.shadow" = FALSE, echo = F, message = F, warning = F)

```
<br>
This repository contains data, code, and output for a project entitled "Working memory performance in adverse environments: Enhanced, impaired, or intact?". A Stage 1 snapshot of the project has been submitted to [Peer Community in Registered Reports (PCI-RR)](https://rr.peercommunityin.org/).

@@

knitr::knit_print(flextable::flextable(proj_history) |> 
  flextable::autofit() |> 
  flextable::compose(
    j = "milestone",
    value = flextable::as_paragraph(
      flextable::hyperlink_text(x = milestone, url = milestone_link)
    )
  ) |> 
  flextable::compose(
    j = "link",
    value = flextable::as_paragraph(
      flextable::hyperlink_text(x = "Click here", url = commit_link)
    )
  ) |> 
  flextable::delete_columns(c("ref", "milestone_hash", "commit_hash", "files", "merge", "milestone_link", "commit_link")))
```
